---
title: "SurfaceArea_AC"
output: html_document
---
##Load Libraries

```{r}
library(tidyverse)
library(here)
library(stringr)
```

##Read in Data

```{r}
SpeciesA_tf <- read_csv(here("Data/Photogrammetry/tf-data-v1.csv"))
SpeciesA_t0 <- read_csv(here("Data/Photogrammetry/t0-data-v1.csv"))
view(SpeciesA_t0)
```

##Wrangle Data

```{r}
SpeciesA_tf_clean <- SpeciesA_tf %>%
  mutate(Measurement = if_else(is.na(volume_mm3), "SurfaceArea", "Volume")) %>% #Adding column for what type of measurement it is
  mutate(Treatment = str_extract(model, "[^_]+$")) %>% #Adding column for the treatement group
  drop_na(model) %>%  #Dropping the na rows from the model column
  rename(SA_tf = surface_area_mm2) %>% #renaming the surface area column to add the timepoint 
  rename(V_tf = volume_mm3) %>% #renaiming the surface area column to add the timepoint 
    filter(model != "backup") %>%
select(-chunk, -closed)

SpeciesA_t0_clean <- SpeciesA_t0 %>%
  mutate(Measurement = if_else(is.na(volume_mm3), "SurfaceArea", "Volume")) %>% #Adding column for what type of measurement it is
  mutate(Treatment = str_extract(model, "[^_]+$")) %>% #Adding column for the treatement group
  drop_na(model) %>%  #Dropping the na rows from the model column
  filter(model != "backup") %>% #Remove the rows with backup models
   rename(SA_t0 = surface_area_mm2) %>% #renaming the surface area column to add the timepoint 
  rename(V_t0 = volume_mm3) %>% #renaiming the surface area column to add the timepoint
  select(-chunk, -closed)

JoinedAreaData <- left_join( SpeciesA_t0_clean,SpeciesA_tf_clean, by = join_by(model, Treatment, Measurement))

#Filter out models that do not have TF data
JoinedAreaData <- JoinedAreaData %>%
  filter(!model %in% c("A13_1_3SP","Copy of A13_1_3SP",
"A14_1_3SP", "Copy of A14_1_3SP",
"A15_1_3SP","Copy of A15_1_3SP",
"A16_1_3SP", "Copy of A16_1_3SP",
"A09_1_FAKE", "Copy of A09_1_FAKE",
"A10_1_FAKE", "Copy of A10_1_FAKE",
"A11_1_FAKE", "Copy of A11_1_FAKE",
"A12_1_FAKE", "Copy of A12_1_FAKE",
"A05_1_6SP", "Copy of A05_1_6SP",
"A06_1_6SP", "Copy of A06_1_6SP",
"A07_1_6SP","Copy of A07_1_6SP",
"A08_1_6SP", "Copy of A08_1_6SP" )) %>% #Filtering out all models that do not have tf data
    filter(!grepl("^b", model, ignore.case = TRUE)) %>% #filtering out all b models
  filter(!grepl("^Copy of b", model, ignore.case = TRUE)) %>%
  #Filtering out all copy of b models
    mutate(FragID = str_extract(model, "[A-Za-z]\\d+")) %>%
  relocate(FragID, .after = 1) %>% #Moving to different order of columns
  relocate(Treatment, .after =2) %>%
  relocate(Measurement, .after =3)
```

Making growth data by looking at the difference between t_final and t-initial surface area and volume

```{r}
GrowthData <- JoinedAreaData %>%
  mutate(DeltaSA = (SA_tf - SA_t0)/100) %>% #Find the growth data and divide by 100 to change to cm2
  mutate(DeltaV = (V_tf - V_t0)/1000) %>%#Divide by 100 to change to cm3
  filter(DeltaSA > 0) %>% #Getting rid of negative values **Should check these models later
  filter(DeltaV > 0) 
  
  


GrowthData$model[is.na(GrowthData$DeltaSA)] #Listing which model names we are missing tf data for 

GrowthData <- GrowthData %>% filter(!is.na(DeltaSA)) #filtering out the remaining models that do not have tf data **We need to double check this 
```

Making a function to find standard error 

```{r}

se_fun <- function(x) {
  n <- sum(!is.na(x))
  if (n <= 1) return(NA_real_)
  sd(x, na.rm = TRUE) / sqrt(n)
}
```


Generate Summary Data for each treatment group

```{r}
GrowthSummary <- GrowthData %>%
  group_by(Treatment) %>% #Group by treatment to take averages across treatment groups etc. 
  summarise(
    N_SA = sum(!is.na(DeltaSA)),
    N_V = sum(!is.na(DeltaV)),
    DeltaSA_avg = mean(DeltaSA), 
    DeltaV_avg = mean(DeltaV), 
    se_SA = se_fun(DeltaSA), 
    se_V = se_fun(DeltaV))
```

Reorder the data based on mean values and combine it with our data set to plot it

```{r}
GrowthDataOrdered <- GrowthData %>% left_join(GrowthSummary, by = "Treatment") %>%
  mutate(Treatment = fct_reorder(Treatment, DeltaSA_avg))
```

Plot the data
We will make geom jitter plot with stat summary in it 

```{r}
SurfaceAreaPlot <- ggplot() + #Use ggplot to make the graphs
  geom_jitter(data = GrowthDataOrdered, aes(x = Treatment, y = DeltaSA, color = FragID),  #Geom jitter with treatment on the x axis and change in surface area on the y axis in cm, we want each individual fragment to be colored
              width = 0.15, alpha = 0.8) + #This is setting the size of points
  # stat_summary(data = GrowthDataOrdered, aes(x = Treatment, y = DeltaSA)
  geom_errorbar(data = GrowthSummary, aes(x = Treatment, ymin = DeltaSA_avg - se_SA, ymax = DeltaSA_avg + se_SA), #Making the error bars on the graph fromt eh summary stats that we made above
                width = 0.2, linewidth = 0.6) + #Size of the error bars
  geom_point(data = GrowthSummary, aes(x = Treatment, y = DeltaSA_avg), size = 2) + #This is the point of the average of the growth values
  labs(y = expression("Change in Surface area cm"^2), #changing the y-axis title 
       x = "Treatment Group") + #changing the x-axis title 
  
  theme_bw(base_size = 22) #Theme of the plot set to black and white and size of font to 22

SurfaceAreaPlot

ggsave(here("Output", "SurfaceAreaChange_Jitter.pdf"), SurfaceAreaPlot, h = 5, w = 10) #Save the graph into a folder, can ignore 

```


Now we can do the same for Volume

```{r}
VolumePlot <- ggplot() + #Use ggplot to make the graphs
  geom_jitter(data = GrowthDataOrdered, aes(x = Treatment, y = DeltaV, color = FragID),  #Geom jitter with treatment on the x axis and change in volume on the y axis in cm, we want each individual fragment to be colored
              width = 0.15, alpha = 0.8) + #This is setting the size of points
  
  geom_errorbar(data = GrowthSummary, aes(x = Treatment, ymin = DeltaV_avg - se_V, ymax = DeltaV_avg + se_V), #Making the error bars on the graph fromt eh summary stats that we made above
                width = 0.2, linewidth = 0.6) + #Size of the error bars
  geom_point(data = GrowthSummary, aes(x = Treatment, y = DeltaV_avg), size = 2) + #This is the point of the average of the growth values
  labs(y = expression("Change in Volume cm"^3), #changing the y-axis title 
       x = "Treatment Group") + #changing the x-axis title 
  
  theme_bw(base_size = 22) #Theme of the plot set to black and white and size of font to 22

VolumePlot

ggsave(here("Output", "VolumeChange_Jitter.pdf"), VolumePlot, h = 5, w = 10) #Save the graph into a folder, can ignore 

```

